Illusion Game Validation (Study 1)

### 2022-08-04 study1.Rmd
study0

>>>>

```{r eval=FALSE, message=FALSE, warning=FALSE, cache=FALSE, include=FALSE}
# Exploratory 
# ============

# ISI
model <- glmmTMB::glmmTMB(Error ~ Illusion_Type * poly(ISI, 2) + (1|Participant),
                    data=mutate(df, Illusion_Type = as.factor(Illusion_Type)),
                    family="binomial")

estimate_relation(model, at = c("ISI", "Illusion_Type")) |>
  ggplot(aes(x = ISI, y = Predicted, color="Illusion_Type")) +
  geom_line()

model <- glmmTMB::glmmTMB(RT ~ Illusion_Type * poly(ISI, 2) + (1|Participant),
                    data=mutate(df, Illusion_Type = as.factor(Illusion_Type)) |>
                      filter(Error == 0))

estimate_relation(model, at = c("ISI", "Illusion_Type")) |>
  ggplot(aes(x = ISI, y = Predicted, color=Illusion_Type)) +
  geom_line()

# Difficulty - Link type
ps <- list()
for(illusion in c("Delboeuf", "Ebbinghaus", "Rod-Frame", "Poggendorff", 
"Vertical-Horizontal", "Zöllner", "Müller-Lyer", "Ponzo", 
"Contrast", "White")) {
  data <- filter(df, Illusion_Type == illusion, Illusion_Strength == 0)
  model <- mgcv::gamm(Error ~ s(Illusion_Difference, k=4),
                      random = list(Participant = ~1),
                      data=data,
                      family="binomial")

  ps[[illusion]] <- estimate_relation(model, 
                                     at = list(Illusion_Difference = unique(data$Illusion_Difference))) |>
    ggplot(aes(x = Illusion_Difference, y = Predicted)) +
    geom_bar(stat="identity", alpha=0.3) +
    geom_line() +
    ggtitle(illusion)
}

see::plots(ps)

```
